The problem and promise of scale in animal social multilayer networks

### 2020-08-27 paper/manuscript.Rmd
minor edits

We generated multilayer networks across a series of social distance thresholds
for group assignment. Social distance thresholds (5, 25, 50, 75, 100, 250 and
500 m) represent a range of sensory modalities of caribou from visual 
to olfactory and auditory. Multilayer networks consisted
of the social association between `r DT[, uniqueN(get(idcol))]` individuals
across three habitat layers (foraging, forest, and open) for the entire study
period. At the finest scale, individuals within 5 m of one another were
considered in the same group, whereas at the coarsest scale, individuals within
500 m of one another were considered in the same group. Increasing social
distance threshold is a proxy for potential behavioural interactions (eg. vocal communication)
that occur
across these distances. For every social distance threshold, we calculated
individual graph strength within each habitat layer, and edge overlap and
multidegree across habitat layers.

### Spatial scale
To assess the influence of land cover spatial scale, we aggregated the land cover raster
using the R package `grainchanger` [@Graham_2019] across a series of scales 
(100 - 1000 m by steps of 100 m) using a modal moving window method [@Graham_2019a]. 
We assume 30 m and 100 m represents fine-scale decision making
for caribou [@Mayor_2007], while 500 - 1000 m represents the scale at which
caribou tend to select and avoid habitat [@Bastille_2018]. Multilayer networks
consisted of the social associations between `r DT[, uniqueN(get(idcol))]`
individuals across three habitat layers (foraging, forest and open) for the
entire study period. For each land cover resolution, we calculated individual
graph strength within each habitat layer, and edge overlap and multidegree
across habitat layers.

### Temporal scale
#### Time windows 
We used a temporal multilayer network to assess the seasonality of caribou
sociality. Multilayer networks consisted of the social associations between 
`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods from the
entire study period. For each time window, we calculated
individual graph strength within each time window, and edge overlap and
multidegree across time windows.

#### Number of observations
Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks,
ranging from directly observed to remotely sensed [@Davis_2018; @Webber_2019].
Remotely sensed GPS data are commonly collected at a fixed rate, e.g. every $x$
minutes or hours, continuously throughout the study period. Fix rate is a
reflection of number of observations an individual would have been observed and
recorded in traditional ethological studies. To investigate the influence of
number of observations, we generated multilayer networks of social association
between `r DT[, uniqueN(get(idcol))]` individuals across three habitat layers
(foraging, forest, and open) using $n$ randomly selected observations. We first
generated a maximum of 1000 timesteps and iteratively used $n$ of these ($n$ =
10 - 1000 observations by steps of 10), to ensure previously included timesteps,
and resulting associations, were accumulated with subsequent observations to
mimic collection of observational data. Within each multilayer network with $n$
observations, we calculated individual graph strength and multidegree. We
calculated edge overlap across the entire series of networks to determine
proportion of total edges as number of observations increased.

>>>>

We generated multilayer networks across a series of social distance thresholds
for group assignment. Social distance thresholds (5, 25, 50, 75, 100, 250 and
500 m) represent a range of sensory modalities of caribou from visual 
to olfactory and auditory. Multilayer networks consisted
of the social association between `r DT[, uniqueN(get(idcol))]` individuals
across three habitat layers (foraging, forest, and open) for the entire study
period. At the finest scale, individuals within 5 m of one another were
considered in the same group, whereas at the coarsest scale, individuals within
500 m of one another were considered in the same group. Increasing social
distance threshold is a proxy for potential behavioural interactions 
that occur across these distances (eg. grooming through vocal communication). 
For every social distance threshold, we calculated
individual graph strength within habitat layers, and edge overlap and
multidegree across habitat layers.

### Spatial scale
To assess the influence of land cover spatial scale, we aggregated the land cover raster
using the R package `grainchanger` [@Graham_2019] across a series of scales 
(100 - 1000 m by steps of 100 m) using a modal moving window method [@Graham_2019a]. 
We assume 30 m and 100 m represents fine-scale decision making
for caribou [@Mayor_2007], while 500 - 1000 m represents the scale at which
caribou tend to select and avoid habitat [@Bastille_2018]. Multilayer networks
consisted of the social associations between `r DT[, uniqueN(get(idcol))]`
individuals across three habitat layers (foraging, forest and open) for the
entire study period. For each land cover scale, we calculated individual
graph strength within habitat layers, and edge overlap and multidegree
across habitat layers.

### Temporal scale
#### Time windows 
We used a temporal multilayer network to assess the seasonality of caribou
sociality. Multilayer networks consisted of the social associations between 
`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods from the
entire study period. For each time window, we calculated
individual graph strength within time windows, and edge overlap and
multidegree across time windows.

#### Number of observations
Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks,
ranging from directly observed to remotely sensed [@Davis_2018; @Webber_2019].
Remotely sensed GPS data are commonly collected at a fixed rate, e.g. every $x$
minutes or hours, continuously throughout the study period. Fix rate is a
reflection of number of observations an individual would have been observed and
recorded in traditional ethological studies. To investigate the influence of
number of observations, we generated multilayer networks of social association
between `r DT[, uniqueN(get(idcol))]` individuals across three habitat layers
(foraging, forest, and open) using $n$ randomly selected observations. We first
selected a maximum of 1000 timesteps and iteratively used $n$ of these ($n$ =
10 - 1000 observations by steps of 10), to ensure previously included timesteps,
and resulting associations, were accumulated with subsequent observations to
mimic collection of observational data. Within each multilayer network with $n$
observations, we calculated individual graph strength and multidegree. We
calculated edge overlap across the entire series of networks to determine
proportion of total edges as number of observations increased.
